Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-05-23 compact_boson.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow
[draft] App. G done

\todo[inline]{Remember to mention in the main text, winding sectors have no contribution}

In this appendix, we address the issue of winding modes of compact bosons. In the main text, we exclusively work with the oscillator modes of free bosons. Here, we shall show that winding modes for compactified bosons will have no contribution to the fidelity or Loschmidt echo in the leading order. Therefore, our results are ready to be applied in the case where two compactified bosons of different radii are connected by a conformal interface\cite{PhysRevLett.118.136801}. \todo[inline]{say intuition why not matter, mention application to Laughlin, etc.}

@@

\subsection{Mode Expansion of Compact Boson}
Suppose the boson is compactified as $\phi =  \phi + 2\pi R$, then mode expansion will have zero mode
\begin{equation}
\begin{aligned}
\phi( x, t ) &= \phi_0 - \frac{2\pi m R}{L}x + \frac{\pi_0}{gL} t  + \frac{i}{\sqrt{4 \pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+ \bar{a}_{n} e^{2\pi i n(x+t)/L})\\  
&= \phi_0 - \frac{2\pi m R}{L}x + \frac{n}{gLR} t  +  \frac{i}{\sqrt{4 \pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+ \bar{a}_{n} e^{2\pi i n(x+t)/L})\\ 
\end{aligned}
\end{equation}
where the conjugate momentum $\pi_0$ takes discrete eigenvalues $\frac{n}{R}$. In the holomorphic coordinates
\begin{equation}
z = \exp( 2 \pi i \frac{t - x}{L}) \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L})
\end{equation}
the mode expansion becomes
\begin{equation}
\label{eq:boson-mode-exp}
\begin{aligned}
\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } \\
&-i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n } 
\end{aligned}
\end{equation}
We further identify 
\begin{equation}
\begin{aligned}
  a_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right) \\
  \bar{a}_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)
\end{aligned}
\end{equation}
and then 
\begin{equation}
i \partial_z \phi =  \sum_n \frac{1}{\sqrt{4\pi g}} a_n z^{-n-1} 
\end{equation}

@@

\todo[inline]{Say the caveat, where is the bounadry}

We recall that the conformal boundary condition can be written as
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}
\end{equation}
where the scattering matrices are given in Eq.~\eqref{eq:S1_S2}. The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, and the $\partial_x \phi^2$ term changes sign, we therefore have 
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_+\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_-\phi^2
\end{pmatrix}
\end{aligned}
\end{equation}
Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
\bar{a}_n^1\bar{z}^{-n}\\
\bar{a}_n^2\bar{z}^{-n}
\end{pmatrix}
=S(\theta)
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
a_n^1{z}^{-n}\\
a_n^2{z}^{-n}
\end{pmatrix}
\end{aligned}
\end{equation}
As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
\begin{equation}\begin{aligned}
a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
\end{aligned}\end{equation}
The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}.

@@

For the amplitude between the same boundary states $\lambda_1=\lambda_2$, we have the winding mode contribution as
\begin{equation}
\begin{aligned}
\label{eq:Z0}
Z_0 = \sum_{S_1 } g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
\end{aligned}
\end{equation}
In the limit $\beta\rightarrow\infty$, Eq.~\eqref{eq:Z0} can be approximated by a simple two dimensional integral
\begin{equation}\begin{aligned}
Z_0\approx g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } (\sqrt{\beta})^2\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}\propto\beta
\end{aligned}\end{equation}
Thus the winding mode will contribute at most a $\ln\beta$ term to the free energy. Compared to the result in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}, we conclude that the winding mode contribution is negligible in the large $\beta$ limit.

>>>>

In this appendix, we address the issue of winding modes of compact bosons. In the main text, we have exclusively worked with the oscillator modes of free bosons. Here, we shall show that winding modes for compactified bosons will have no contribution to the fidelity or Loschmidt echo in the leading order. Therefore, our results are ready to be applied in the case where two compactified bosons of different radii are connected by a conformal interface\cite{PhysRevLett.118.136801}. \todo[inline]{say intuition why not matter, mention application to Laughlin, etc.}

@@

\subsection{Mode Expansion of Compact Boson}
Suppose the boson is compactified as $\phi =  \phi + 2\pi R$, then mode expansion will have zero mode

\begin{widetext}
\begin{equation}
\begin{aligned}
\phi( x, t ) &= \phi_0 - \frac{2\pi m R}{L}x + \frac{\pi_0}{gL} t  + \frac{i}{\sqrt{4 \pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+ \bar{a}_{n} e^{2\pi i n(x+t)/L})\\  
&= \phi_0 - \frac{2\pi m R}{L}x + \frac{n}{gLR} t  +  \frac{i}{\sqrt{4 \pi g}}\sum_{n\neq0}\frac{1}{n}(a_ne^{2\pi i n(x-t)/L}+ \bar{a}_{n} e^{2\pi i n(x+t)/L})\\ 
\end{aligned}
\end{equation}
where the conjugate momentum $\pi_0$ takes discrete eigenvalues $\frac{n}{R}$. In the holomorphic coordinates
\begin{equation}
\label{eq:zzbar}
z = \exp( 2 \pi i \frac{t - x}{L}) \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L})
\end{equation}
the mode expansion becomes
\begin{equation}
\label{eq:boson-mode-exp}
\begin{aligned}
\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } -i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n } 
\end{aligned}
\end{equation}
\end{widetext}
We further identify 
\begin{equation}
\begin{aligned}
  a_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right) \\
   \bar{a}_0 &= \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)
  \end{aligned}
\end{equation}
and then 
\begin{equation}
\begin{aligned}
i \partial_z \phi =  \sum_n \frac{1}{\sqrt{4\pi g}} a_n z^{-n-1} 
\end{aligned}
\end{equation}

@@

Following the treatment of boundary CFT in Ref.~\onlinecite{di_francesco_conformal_1997}, we shall quantize the theory by imposing \emph{equal-time} commutator for $a_n$ and $\bar{a}_n$ in Eq.~\eqref{eq:boson-mode-exp}. The conformal boundary state will be defined on a constant time slice, say $t=0$. For the permeable wall connecting two compactified bosons, this results in folding $t\rightarrow-t$ rather than $x\rightarrow-x$ as in the main text. Since the two cases are {\bf T}-dual to each other, the results are not affected.

%Before we invoke the folding trick, we need to note one important caveat here. In the usual treatment of boundary CFT, for example in , the field is quantized on the real axis. As emphasized in Sec.~\ref{sec:bosonic_conformal_interface}, the gluing condition becomes an operator identity of creation and annihilation operators, which is valid \emph{only} when acting on the conformal boundary states.

We recall that the gluing condition is written as
\begin{equation}\begin{aligned}
\label{eq:def_M}
\begin{pmatrix}
\partial_t\phi^1\\
\partial_x\phi^1
\end{pmatrix}_{t=0^-}
=M\begin{pmatrix}
\partial_t\phi^2\\
\partial_x\phi^2
\end{pmatrix}_{t=0^+}
\end{aligned}\end{equation}
where the derivatives are evaluated at the appropriate limit. In this appendix, we shall take the definition $x^\pm=x\pm t$ and $\partial_\pm=\partial_x\pm\partial_t$. Therefore we establish the scattering matrix as
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}
\end{equation}
%The folding sends $\phi^2(x)\rightarrow\phi^2(-x)$ for $x<0$, and the $\partial_x \phi^2$ term changes sign, we therefore have 
%\begin{equation}
%\begin{aligned}
%\label{eq:def_S_in_app_2}
%\begin{pmatrix}
%\partial_+\phi^1\\
%\partial_+\phi^2
%\end{pmatrix}
%=S(\theta)
%\begin{pmatrix}
%\partial_-\phi^1\\
%\partial_-\phi^2
%\end{pmatrix}
%\end{aligned}
%\end{equation}
%Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
%\begin{equation}
%\begin{aligned}
%\label{eq:def_S_in_app_2}
%\sum_{n\in\mathbb{Z}}
%\begin{pmatrix}
%\bar{a}_n^1\bar{z}^{-n}\\
%\bar{a}_n^2\bar{z}^{-n}
%\end{pmatrix}
%=S(\theta)
%\sum_{n\in\mathbb{Z}}
%\begin{pmatrix}
%a_n^1{z}^{-n}\\
%a_n^2{z}^{-n}
%\end{pmatrix}
%\end{aligned}
%\end{equation}
%As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
%\begin{equation}\begin{aligned}
%a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
%\end{aligned}\end{equation}
%The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}. 
The folding sends $\phi^2(t)\rightarrow\phi^2(-t)$ for $t<0$, and the $\partial_t \phi^2$ term changes sign, we therefore have 
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_+\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_-\phi^2
\end{pmatrix}
\end{aligned}
\end{equation}
Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
\bar{a}_n^1\bar{z}^{-n}\\
a_n^2z^{-n}
\end{pmatrix}
=-S(\theta)
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
a_n^1{z}^{-n}\\
\bar{a}_n^2\bar{z}^{-n}
\end{pmatrix}
\end{aligned}
\end{equation}
As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
\begin{equation}\begin{aligned}
a^i_n-(-S^{-1}_{ij})\bar{a}^j_{-n}=0
\end{aligned}\end{equation}
The solution of the $n \neq 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}, with an extra minus sign. Following our boundary state calculation in the main text, it is clear that this extra minus sign, which is the result of {\bf T}-duality, does not affect our conclusion.

@@

For the amplitude between the same boundary states $\lambda_1=\lambda_2$, we have the winding mode contribution as
\begin{equation}
\begin{aligned}
\label{eq:Z0}
Z_0 = \sum_{S_1 } g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
\end{aligned}
\end{equation}
In the limit $\beta\rightarrow\infty$, Eq.~\eqref{eq:Z0} can be approximated by a simple two dimensional integral
\begin{equation}\begin{aligned}
Z_0\approx g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} }\beta\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}
\end{aligned}\end{equation}
The integral is a constant, thus the winding mode will contribute at most a $\ln\beta$ term to the free energy. Compared to the result in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}, we conclude that the winding mode contribution is negligible in the large $\beta$ limit.
